---
title: "Cascade Impactor"
author: "Magali Blanco"
date: "1/18/2018"
output: word_document
---
comparing collocated Dylos and cascade impactors Sept 28-30, Locations A & C, below the canopy

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(reshape2)

```

Mylar Data
```{r}
MylarData <- read_excel("~/Everything/School/PhD_UW/Courses/2. Winter 18/ENVH 595 Yost RR/Data/Cascade Impactor/Eddie/MylarData.xls")

#only include relevant columns 
Mylar <- MylarData[c("sprayer", "collectdate", "samp_id", "height_m", "dist_m", "sampvol_l", "stage", "ug", "below_loq", "drift_ml", "conc_ml_l")] #ml drift vol / l vol sampled 

#there are no negataive "ug" values to adjust for (e.g. substitute LOQ, etc.)

#convert "conc_ml_l" to "conc_ug_cm3"
## ml numerator to ug: * water density 1 g/ml * (10^6 ug/g) = ug/ml density
## l denominator to cm3: * (1 L / 10^3 cm3)
Mylar$conc_ug_cm3 <- Mylar$conc_ml_l*1*(10^6)/(10^3)

#relabel sprayers & only use AFA 
Mylar$sprayer <- ifelse(Mylar$sprayer=="pak", "AFA", ifelse(Mylar$sprayer=="quantum", "MFT", "turbo"))

#only include AFA data
Mylar <- Mylar[Mylar$sprayer=="AFA",]

#only use Sept 2016 values
Mylar <-Mylar[Mylar$collectdate >="2016-09-28" & Mylar$collectdate <="2016-09-30",]

#change date name
colnames(Mylar)[colnames(Mylar) =="collectdate"] <- "ObservedDate"

#add cutpoint associated with each stage
Mylar$cut_um <- ifelse(Mylar$stage==1, 21.3, ifelse(Mylar$stage==2, 14.8, ifelse(Mylar$stage==3, 9.8, ifelse(Mylar$stage==4, 6, ifelse(Mylar$stage==5, 3.5, ifelse(Mylar$stage==6, 1.55, ifelse(Mylar$stage==7, 0.93, ifelse(Mylar$stage==8, 0.52,0))))))))

#label locations
Mylar$Location <- ifelse(Mylar$dist_m==11, "A", "C")

#only keep necessary columns
Mylar <- Mylar[c("ObservedDate", "sprayer", "Location", "cut_um", "conc_ug_cm3")]
colnames(Mylar) <- c("Date", "Sprayer", "Location", "Cut_um", "Conc_ug_cm3")

#add mass concentrations >9.8 um to match Dylos highest cut point of >10 um
Mylar_below9.8 <- Mylar[Mylar$Cut_um<9.8,]

Mylar_above9.8 <- Mylar[Mylar$Cut_um>=9.8,]
Mylar_above9.8 <- aggregate(data=Mylar_above9.8, Conc_ug_cm3~ Date + Sprayer + Location, sum)
Mylar_above9.8$Cut_um <- 9.8

Mylar <- rbind(Mylar_below9.8, Mylar_above9.8)

Mylar$Sampler <- factor("Mylar")

# 3 days x 2 loc/dy * 6 stages/loc = 36 data pts
```


Dylos Data
```{r}
# 3 dys x 2 loc/dy x 4 bins/loc = 24 data points

Dylos <- read_csv("~/Everything/School/PhD_UW/Courses/2. Winter 18/ENVH 595 Yost RR/Data/Dylos/SprayEvents180114.csv")
 
#select only sept dates, loc A & C, Height Below, Event != control,   ; specific columns
Dylos <- Dylos[c(Dylos$Date != "6/10/16" & (Dylos$Location=="A" | Dylos$Location=="C") & Dylos$Height=="Below" & Dylos$Event != "Control"), c("Date", "Sprayer", "Location","PMC_bin0.5","PMC_bin1.0","PMC_bin2.5", "PMC_bin10.0" )] #  "Event_PMC"

# make bin size size & PMC long format
Dylos <- melt(Dylos, id.vars=c("Date", "Sprayer", "Location"))

#rename columns to match Mylar_PMC
colnames(Dylos) <- c("Date", "Sprayer", "Location", "Cut_um", "Conc_ug_cm3")

#format columns
Dylos$Cut_um <- ifelse(Dylos$Cut_um=="PMC_bin0.5", 0.5, ifelse(Dylos$Cut_um=="PMC_bin1.0", 1.0, ifelse(Dylos$Cut_um=="PMC_bin2.5", 2.5, 10.0)))

Dylos$Date <- as.Date(Dylos$Date, "%m/%d/%y")

Dylos <- aggregate(Conc_ug_cm3 ~ Date + Sprayer + Location + Cut_um, data=Dylos, sum)
 
Dylos$Date <- as.factor(Dylos$Date)

Dylos$Sampler <- factor("Dylos")

```

merge Mylar & Dylos data
```{r}
PMC <- rbind(Mylar, Dylos)

```



# Plots 
```{r}



ggplot(data=PMC, aes(x=Cut_um, y= Conc_ug_cm3, color=Sampler)) + geom_point() + ylim(0,.0010)


#geom_point() # #x=Cut_um,  Conc_ug_cm3




```



Cumulative Probability plot 
```{r}

#cumulative probability plot of PMC
ggplot(data=PMC, aes(x=Conc_ug_cm3, colour=Sampler)) + stat_ecdf() + labs(y="Cumulative Probability", x= "Concentration (ug/cm3)")


```





geom_histogram, geom_freqpoly, stat_ecdf

? usefull??  histogram
```{r}

#histogram 
ggplot(data=PMC, aes(x=Conc_ug_cm3, colour=Sampler)) + geom_freqpoly()  #geom_point() # #x=Cut_um,  Conc_ug_cm3
 #######

```










------------- old plots -------------
# # EXAMPLE: AFA, loc A, 9/28
# ggplot(data=PMC[c(PMC$Sprayer=="AFA" & PMC$Location=="A" & PMC$Date=="2016-09-28" ),], aes(x=Cut_um, y= Conc_ug_cm3, color=Sampler)) + geom_point()#geom_point() # #x=Cut_um,  Conc_ug_cm3

